Empirical normative theories

### 2020-08-02 simple.tex
Slightly simpler def of empirical theories.

\section{Additive single-answer empirical theories}
\subsection{Definition}
\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton). 
Given $\ar \in \allargs$, define $\df(\ar) \subseteq \powersetz{\alldargs}$ as $\df(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)}$. 
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
Given any $\ar \in \allargs$ and $\dargs \in \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
Define $\dfp \subseteq \allargs × \allargs$ as $\forall \ar \in \allargs: \dfp(\ar) = \set{\ar + \dargs \suchthat \dargs \in \df(\ar)}$.

\begin{remark}
	Equivalently, $\df(\ar_0) = \powersetz{\dbeatsinv \circ \gbeatsinv}$. 
	First, $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{\dbeatsinv \circ \gbeatsinv}$. 
	Indeed, $\ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$, hence, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\dargs ≠ \emptyset$; and $\ard \in \dargs$ thus $\ard \dbeats \ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$. 
	Second, $\dargs \in \powersetz{\dbeatsinv \circ \gbeatsinv} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$. 
	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{remark}

@@

>>>>

\section{Additive single-answer empirical theories}
\subsection{Definition}
\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton). 
Define $\df: \allargs → \powersetz{\allargs}$ as $\df = \dbeatsinv \circ \gbeatsinv$.
Given $\ar \in \allargs$, $\df(\ar)$ denotes the \emph{fragments defending $\ar$}. 
In other words, given $\ard \in \dargs$ and $\ar_0 \in \allargs$, $\ar_2 \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ar_2 \dbeats \ar_1 \gbeats \ar_0$.
A \emph{coalition defending $\ar$} is any element of $\powersetz{\df(\ar)}$.
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \powersetz{\df(\ar)}) → \allargs$.
Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
Given any $\ar \in \allargs$, define $\dfp(\ar)$, the \emph{defenders of $\ar$}, as $\dfp(\ar) = \set{\ar + \dargs \suchthat \emptyset ≠ \dargs \subseteq \df(\ar)}$.

@@

\begin{remark}
	$\df'(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$. 
	First, $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{\dbeatsinv \circ \gbeatsinv}$. 
	Indeed, $\ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$, hence, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\dargs ≠ \emptyset$; and $\ard \in \dargs$ thus $\ard \dbeats \ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$. 
	Second, $\dargs \in \powersetz{\dbeatsinv \circ \gbeatsinv} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$. 
	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{remark}
